---
title: "p8105_hw6_kpc2124"
author: "Kristi Chau"
date: "11/19/2019"
output: github_document
fig_caption: yes
latex_engine: xelatex
header-includes:
  - \usepackage{floatrow}
  - \floatsetup[figure]{capposition=top}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

library(tidyverse)
library(knitr)
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
library(viridis)
library(modelr)

set.seed(1)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal())
```

## Problem 1

```{r}
bwt = 
  read.csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    frace = ordered(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace),
    mrace = ordered(mrace)
  )
  ## %>% skimr::skim()
```

Found no missing data after running the `skim` function.

Model 1: I modeled `wtgain` and `smoken` as a linear model with `bwt` because `bwt` is a continuous variable.

It has been reported that not gaining enough weight during pregnancy is a risk factor for having a low birthweight baby. Additionally, smoking during pregnancy can possibly confound the association between gaining weight during pregnancy and infant birthweight because it is associated with both weight gain and infant weight, and smoking is unlikely to be a consequence of weight gain.

```{r}
bwt_fit = 
  lm(bwt ~ wtgain + smoken, data = bwt)
```

```{r}
bwt_fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  kable(digits = 3, caption = "Modeling the association between infant birthweight and weight gain and number of cigarettes smoked during pregnancy")
```

It appears that for every 1 pound mothers gained during pregnancy, infant birthweight increased by 11.68 grams, after adjusting for number of cigarettes smoked per day during pregnancy.

For every 1 daily cigarette during pregnancy increase, infant birthweight dropped by 5.70 lbs.

```{r}
bwt %>% 
  modelr::add_residuals(bwt_fit) %>% 
  modelr::add_predictions(bwt_fit) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_violin() +
  labs(
    x = "Fitted Values",
    y = "Residuals",
    title = "Model residuals plotted against fitted values"
  )
```

It appears there is significant error around fitted values of 3100. However, there is also a significant bulk of data around residuals = 0.

Compare to 2 other models:

Model 2: Using length at birth (blength) and gestational age (gaweeks) as predictors (main effects only)

Model 3: Using head circumference (bhead), length (blength), sex (babysex), and all interactions (including the three-way interaction) between these

```{r}
cv_df = 
  crossv_mc(bwt, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_results = 
  cv_df %>% 
  mutate(
    fit1 = map(.x = train,~lm(bwt ~ wtgain + smoken, data = .x)),
    fit2 = map(.x = train,~lm(bwt ~ blength + gaweeks, data = .x)),
    fit3 = map(.x = train,~lm(bwt ~ bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x)), 
    rmse_fit1 = map2_dbl(.x = fit1, .y = test, ~rmse(.x,.y)),
    rmse_fit2 = map2_dbl(.x = fit2, .y = test, ~rmse(.x,.y)),
    rmse_fit3 = map2_dbl(.x = fit3, .y = test, ~rmse(.x,.y))
  )
```

```{r}
cv_results %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() + 
  labs(
    x = "Model",
    y = "Root Mean Squared Errors (RMSEs)",
    title = "Comparison of cross-validated prediction error"
  )
```

We see from this plot that the best fitting model was model 3, which modeled head circumference (bhead), length (blength), sex (babysex), and all interactions among these variables. Model 2 (length at birth (blength) and gestational age (gaweeks) as predictors) had an okay fit, while my model (mother's weight gain during pregnancy (wtgain) and cigarettes smoked during pregnancy (smoken)) was not a good fit and had a very high prediction error.



## Problem 2

```{r, message = FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities (r-squared and log(b0*b1)).

```{r}
r_squared = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance),
    ) %>% 
  select(-strap,-models) %>% 
  unnest(results) %>% 
  select(.id,r.squared)

log_b = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results2 = map(models, broom::tidy),
    ) %>% 
  select(-strap,-models) %>% 
  unnest(results2) %>% 
  select(.id, term, estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  mutate(log_b = log(`(Intercept)` * tmin))
```

Plot the distribution of your estimates
```{r}
r_squared %>% 
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(x = "R^2")
```

It appears that the distribution of the r-squared is somewhat left-skewed, with a few outliers pulling it toward 0.87 on the left. The observations peak around 0.9125. 

```{r}
log_b %>% 
  ggplot(aes(x = log_b)) +
  geom_density()
```

The distribution of the log(beta0*beta1) appears to be more normally distributed with a peak around 2.012.

95% confidence intervals
```{r}
r_squared %>% 
  pull(r.squared) %>% 
  quantile(probs = c(0.025,0.975),na.rm = TRUE)
```

The 95% confidence interval of r-squared is (0.8940,0.9271).

```{r}
log_b %>% 
  pull(log_b) %>% 
  quantile(probs = c(0.025,0.975),na.rm = TRUE)
```

The 95% confidence interval of log(b0 * b1) is (1.9660,2.0586).